\chapter*{Acknowledgements}

I would like to take the opportunity to thank to all the people that in one way
or another helped getting through the development of this thesis. First and
foremost, I would like to express my gratitude to my supervisor, Richard
Kempter. He has shown me how to ask questions in science and how to attack the
problems with the arsenal of simplest methods first. Apart from the outstanding
scientific supervision that Richard provided, his patience and methodology have
been a model how to approach and solve problems outside of the academic life. I
would like to specially thank Henning Sprekeler, who initiated the project on
assembly sequences and supported me in making it done. Special thanks to
Nikolaus Maier for providing me with data and for the helpful discussions on
the origin of SWRs.

Many thanks to the people that provided feedback on various parts of this
thesis: Richard Kempter, Henning Sprekeler, Nikolaus Maier, Adam Wilkins,
Roberta Evangelista, Pia Rose, Eric Reifenstein, Nadia Varley, Jos\'{e} Donoso,
and Andr\'{e} Holzbecher.

I would like to thank my officemates over the years for all the positive vibes,
meaningful discussions, and not so meaningful but fun distractions: Paula
Kuokkanen, Jorge Jaramillo, Jos\'{e} Donoso, Thomas McColgan, Martina
Michalikova, Andr\'{e} Holzbecher, Leonidas Eleftheriou. I also thank to all
the ITB-Neuro members for their support, feedback, and for the discussions on
various topics in the science field. You, people generate a unique and friendly
atmosphere!
%thomas for zsh, vim, git and co. help and advices
%jose for the philosophical implications of our work and anatomy
%martina for the mental and physical health program, and the nice trip

Finally, big thanks to my closest friends for the all the implicit support:
Dobri, Svetlio, Pesho, Tosho, Bibi, Stani, Ogi, Sasho, Florian, Dmitry,
Henning, Alex, and Martina. The trips with you have been brutal events that
left irreversible traces in my memory. Last but not least, a deep gratitude to
my family members in Bulgaria, Russia, and Germany for all the support. A
special thank to Ping and Tiona for the motivation, for the patience, and for
making life even more interesting.


