\chapter{Outlook}
%summary
  The aim of this final chapter is to put into perspective the problems that
  have been analysed so far. In particular, what is the relevance of the
  assembly sequence in the framework of the disinhibitory 3-population model?
  Moreover, I openly discuss some ideas that have occurred spontaneously over
  the course of the last few years.
  %in SWRs, of the real replay, preplay..
  %if stuff gets binded to predifined seqs, why and how?

\section{Bridging the assembly sequence model and the 3-population hypothesis}
  Neural assemblies connected in a feedforward manner can explain the replay of
  behaviour sequences observed in the hippocampus. The sequence replay can be
  evoked by an external input cue, or occur spontaneously. As described in
  Chapter~\ref{chap:asss}, a spontaneous replay requires higher
  connectivities between assemblies than the evoked replay. Moreover, the
  spontaneous replay largely depends on the network excitability, and small
  change of the net input can shift to or from spontaneous replay regime. For
  example, a decrease of the total input to the network abolishes spontaneous
  events, while an increase of the input facilitates them. However, such
  circuitry relying on two populations, an excitatory and an inhibitory one,
  cannot account for the inhibitory-evoked SWRs observed \textit{in vitro}
  \citep[e.g.,][]{Schlingloff2014, Kohus2016}. Therefore, in
  Chapter~\ref{chap:swr}, I described a phenomenological model of a hippocampal
  network consisting of 3 populations. The underlying idea is that the
  activation of one inhibitory population activates a disinhibitory circuit,
  leading to a population burst. An ultimate goal, that has not been achieved
  in this thesis, is to combine these two models (e.g., the assembly sequence
  and the 3-population model) into a single framework. Is the high-firing rate
  regime during a population burst going to dramatically decrease the
  connectivities required for a replay?

  A possible limitation of the assembly-sequence model is the fact that it
  relies on `rigid' assemblies of neurons that are uniformly connected among
  themselves. Experimental data about the synaptic organisation in hippocampus,
  as well as in the cortex, shows heavily skewed distributions of synaptic
  strength and connectivity \citep[e.g.,][]{Takahashi2010, Buzsaki2014,
  Cossell2015}. Lognormal distributions of connectivities and synaptic weights
  between neurons would be a more plausible model for a cell assembly. Then, a
  few `central' neurons will fire reliably during assembly activation, while
  the participation of the `periphery' neurons will depend more on the strength
  and the type of input stimulation. To what degree such modification of the
  model will affect the results of sequence replay is not known.
  %different neurons can join the neurons depending on the context, the modalities, and the evoked depth of the concept

\section{Testing the 3-population hypothesis \textit{in vitro}}

  however, is it the ultimate and the only model?
  multiple types of SWs; same or different mechanisms? in vitro ripple can go from 180 to 300 hz
  - buzsaki2015: diff SWs during diff behaviours..
  - in-vitro experiments show various incedences 0.1 to 10?
  - various ripple frequences
  - reference on diff SWs Hofer2015, wasnt there some ref on diff SWRs in vivo?
  - weather it's always the same circuit is not clear, in studies we have to study a particular 
  in-vitro model and treat carefully results from other in-vitro models. Maybe some benchmarks for 
  classifying the type of SW are observed..
  - some epileptic burst can be also classified as SWRs
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  % state of the modelling 
  to understand SWs, these experiments are the key.  measuring the FRs of IN
  populations, refines the parameters of the model, or changes the model
  what are the open questions:
  - we can make models that mimic different behaviours but they will always
  lie on assumptions die to the complexity of the circuit (2pop model can
  already explain gabazine in 2 ways), the way to go is to know how the
  effects on different neural populations pv, pc, dti......

  replay of ASS during SWRs; inhib can modulate which assemblies are played, or at least bias

  Experiment suggestions: -
  - quantify network effects of gabazine:
  - measure and compare PC firing before and during gabazine administration
  - same for PVBC and the mysterious INs
  - identify the INs that inhibit PC firing between events.
  %
  dsad 

  bannon2017: adenosine and hebbian plasticity


\section{Further implications of the disinhibitory circuit}
  %here theta: theta seqs...?
  The 3-population hypothesis is a plausible general mechanism for achieving
  multistability of local networks. Particularly, a disinhibitory pathway can
  lead to a rapid activation of the excitatory network upon command.  Such
  mechanism might underlie the gating of spontaneous activity not only in the
  hippocampus, but also in local cortical networks. \cite{Luczak2013} suggested
  that the sensory cortex is constantly processing the inputs in a background,
  low-firing rate regime, i.e., the `down state'. Upon a top-down request from
  higher-order areas, the sensory cortex switches to an `up state', and thus,
  gates the sensory information upstream. Such up states might be achieved
  through rapid disinhibition.

  A line of research from Brecht lab points out to the plausibility of the
  disinhibitory hypothesis in the cortex. \cite{Brecht2004} has shown that a
  repetitive stimulation of a single pyramidal neurons in the rat motor cortex
  can evoke whisker movement. The stimulation evoked a marked change of pattern
  activity reflected in the field potential and increased firing of the fast
  spiking, putative inhibitory interneurons \citep{Houweling2007, Doron2014}.
  Moreover, stimulation of fast spiking, putative inhibitory interneurons in
  somatosensory cortex led to stronger effects detected in the animal's
  behaviour compared to a stimulation of principal cells \citep{Doron2014}.
  The stimulations were typically followed by a `long-lasting' inhibition of
  firing rates measured in the microcircuit \citep{Doron2014}. However,
  experiments targeting the disinhibitory neurons would address explicitly the
  question of disinhibition in cortical networks.
  
  in hp, similar effects can be achieved also with theta: theta seqs are at particular phase of
  theta, when there is more excitation; are theta seqs intrinsic, maybe not.. not that small time delays
  what is the role the oscillation gamma, ripple?
  givin a particular window of opportunity, when the inputs are also optimized for that window; no need
  to integrate over long intervals, which is not possible
  ripple discretizes the float of information
  discrete assemblies are more efficient ? or there is always some level of interplay between assemblies?
  embedded assemblies? or multiple assemblies that integrate inputs and act like neurons; in the case of ripples they are more prominent

  participation or does it only give windows of opportunity for firing?
  information on the order of PC firing can be transfered also through the inhib population.
  giving certain times during the ripple windows...(ref on inhib propagation of activity norman?)

  % role of ripples
  norman2006: algorithm relying on inhibitory learning that facilitates weak memories
  and punishes the activation of competitor memories

\section{Why hippocampal replay?}
  According to the standard 2-stage memory model, behaviour sequences are
  imprinted in the CA3 recurrent networks upon experience \citep{Marr1971,
  Buzsaki1989}. However, such view has been challenged in the last years as a
  number of reports show that hippocampal replay is not a simple function of
  experience \citep[e.g.,][]{Gupta2010}. Even more explicitly,
  \cite{Dragoi2011, Dragoi2013} showed that sequences are replayed in the
  hippocampus already prior to the first exposure of the environment which
  these sequences represent. Dragoi suggested\footnote{The event was a public
  talk at BCCN-Berlin in 2013?} that the role of CA3 is to create blank
  sequences that are mapped later to experience. \cite{ChengS2013} proposed the
  CRISP model which goes along these lines. According to the model, CA3
  sequences are formed offline prior to utilization due to the maturation of
  newly generated granule cells in the dentate gyrus. During the first exposure
  to the environment, granule cells that carry sparse information about the
  environment are instantly mapped to the CA3 sequences via the mossy fibers.
  While this is a plausible explanation of how the hippocampal input is mapped
  to the blank hippocampal sequences, it is unclear how the hippocampal output
  during the offline replay is mapped back to the context it represents. Such
  mapping would require highly plastic synapses that are able to encode
  information in a single trial of experience. \cite{ChengS2013} hypothesises
  that the internal sequences are mapped back to the context information via
  the feedforward synapses from CA1 to the deep EC layers.

  Many questions remain unanswered to date about the origin and function of the
  hippocampal replay. If sequence replays are intrinsic property of the CA3
  region, then two links have to be created on demand upon learning: context
  --> CA3 sequence; and CA3 sequence --> context.  

  one option is that sequences are there, but elements are attached to the seq,
  this will require much less creation of new synapses and assemblies.
  scale-free assembly with new members joining, then each further replay will
  consolidate the new elements into the assembly...
  
  However, in vivo SWR replays
  might be modulated by external inputs, from EC, or subiculum..  If external
  information drives the replay, then there is no need for rapid hp output
  mapping..?

  Another possible link between the input and the output of the hippocampus can
  also happen in the EC, on the synapses between the superficial and deep
  layers.


here in the last pages, I will track a hypothetical experiment (geist experiment???)
jennifer and oma..

jenifer and oma are heavily connected; in the context of neuroscience, one concept is
likely to evoke the other ; outside of the context, probably not as much connected
  connection between abstract concepts, fast and to the point
  - our linear thinking is kind of boring and limiting. is there a way out?
  conceptualized knowledge is linear; thinking relies on the distributed net of concepts that can bring surprises;
  once we live in the hp, however, it's linear
  implicit knowledge is non-linear
  we linearize and consolidate patches of linearized associations...the resulting network of concepts might be quite complez and of different quality as presented in hp


  distributed...place cells -> grids

%propse experiment: find the cheese neuron in DG and activate it each time animal at a place
%can work with any object neuron, and then associate the object with cheese, and let the animal in that env with virtual object again :)

  probably in hippocampus can become as sparse and sharp as they can. Further downstream (upstreams) assemblies are getting blurrier and more mixed.

  sparse info at the input, then smears out in the cortex but is also sparse in the hp. that's how we create declarative representations or memories of abstract ideas that do are not necessary present to the brain by the sensory system; a place, or a word describing the tree we see. these 
  - the input is not sparse actually, as uniform as it gets

  assembly sequences in simpler neural systems might be more prevailing?

  can the sparseness have a few dimensions, what I mean is that from orientation-maps the further levels of visual processing go to more complex representations that in a way are sparser? are they?

  jennifer aniston neuron..what is the advantage of such coding
  for making a link between abstract concepts (aniston and our grandma), maybe it's good to make this link 
  at the highest abstraction, rather than at the level of subabstractions..

  while my grandma is associated with the house that I used to visit her at,
  with the stories that she used to tell me, or more generally with any memory and experience
  that has numereous emotianal attachments to it and that shapes me as a self.
  jeniffer aniston is connected mostly with some TV show, such as friends or
  other cheesy romantic movie, and possibly with remote memories while seening
  these shows.

  so what happens when i connect my grandma and aniston in a typical mnemonic
  task?

  while revoking their representations, multiple areas in the cortex are boiling
  by igniting assemblies that constitute the mental concepts. These assemblies
  can be distributed over the whole cortex and represent various concepts such
  as events, people, emotions, etc. To create links between this diverse zoo of
  concepts should be a tricky task, prune to errors due to noise.. However, in
  the hippocampus, the representations are on the highest level: between oma
  and aniston; the question is how this connection `backpropagates' to the
  founding concepts. While we don't know the answer to this question, some relatively
  recent finding from the EC might give a hint. Grid cells in EC, major input/output of the hippocampus.


\section{Extension of the assembly}
  %extension of the comp model.
  A more rigid mathematical description has been attempted 
  replay is neither static nor instant; a new mathematical description is necessary
  the linear description was pretty good in the
  parameter space tested in this work
  despite the efforts, more rigid math was not achieved:
  however 2pop is just part of he picture, how it fits with 3pop?



%memory pyramid sprarse-> distributed 
\section{experiments, diff dwr models..}
  % IN vitro model
  why different ripples in ca3 and ca1????
\section{randoms}

  - why thiopental and gabazine have similar effect on incidence despite
  their in a way opposite functions on inhibition; because of toinc inhib?
  both result in release of GABA from the presynaptic cleft?


  %%%%%%%%%%%%%%
  connection with oscillations:
  %%%%%%%%%%%%%%
  here we assume AI state, however the brain likes to oscillate. Different frequency of oscillations are hypotheisised to give a band for communications between assemblies.[ref on communication through resonance]. 

  on fast and slow time scales of learning and plasticity how they match? theta, gama, PP, spwrs

  swr interplay with phase precession

  amazing compression of time, but why hippocampus? for declarative memories, only? look at HM, he was good and happy; decision making was intact, feeling basically everything without the fucking declarative memories. A few example of learned words however show that it's not the hippocampus monopole in learning, although not efficiently. So what else? no time no memory! no memory, no time? 
  it's not the memories that define us per se but the memories can nevertheless change the personality on a slower time scale. without new memories time just passes and we are death at some moment. with memories on the other side we live in the float of life and keep updating our representation of this float in a way that is often beneficial for the survival. and just then we die :). time wasn't worthless whatever the outcome though!

  of course this is only a theory which is being tested and refined over the last years. we keep looking into cracking it and diving deeper, by 

  distal dendrites context, how children cannot separate context with info-> develops with time...
  same assemblies can have different meanings in different contexts..


  mindwandering affects our memories? why not? interesting question! people imagining an learning certain action can do as IF THEY Have done the ac

  hp: thoughts
  - we are taking snapshots of the flow around us and try to integrate them with our
  understanding of the world in our memory
  -there is certain symmetry in time, we are in the middle, and there are 2 directions.
  -time is intimate to us. after getting through the events of the past, we are
  standing in motion in the current moment and moving with variable (but
  positive) speed to the future.
  live without past and without future

  - nakashiba: ca3 output blocked: no learning and less sws (maybe next subsec)
  in the hip
  gridsmm

  ideas for experiments:
  mouse runs in an environment for the first time, place cells are detected and recorded
  check for connectivity, connection strength between themselves, let the mouse explore many many times more
  check again for change in connectivity.
  do this also for grid cells





