
\begin{thebibliography}{}

\bibitem[Abeles, 1991]{Abeles91}
Abeles M (1991{\rm{}})
\newblock {\rm Corticonics: neural circuits of the cerebral cortex}.
\newblock Cambridge, UK: Cambridge UP.

\bibitem[Almeida~Filho {\rm et~al.}, 2014]{AlmeidaFilho2014}
Almeida-Filho DG, Lopes-dos-Santos V, Vasconcelos NA, Miranda JG,
  Tort AB, Ribeiro S (2014{\rm{}})
\newblock An investigation of Hebbian phase sequences as assembly graphs.
\newblock {\rm Front Neural Circuits } 8:34.

\bibitem[Atwood and Wojtowicz, 1999]{Atwood1999}
Atwood HL, Wojtowicz JM (1999{\rm{}})
\newblock Silent synapses in neural plasticity: current evidence.
\newblock {\rm Learn Mem } 6:542--571.

\bibitem[Aviel {\rm et~al.}, 2004]{Aviel2004}
Aviel Y, Horn D, Abeles M (2004{\rm{}})
\newblock Synfire waves in small balanced networks.
\newblock {\rm Neurocomput } 58:123--127.

\bibitem[Aviel {\rm et~al.}, 2003]{Aviel2003}
Aviel Y, Mehring C, Abeles M, Horn D (2003{\rm{}})
\newblock On embedding synfire chains in a balanced network.
\newblock {\rm Neural Comput } 15:1321--1340.

\bibitem[Aviel {\rm et~al.}, 2002]{Aviel2002}
Aviel Y, Pavlov E, Abeles M, Horn D (2002{\rm{}})
\newblock Synfire chain in a balanced network.
\newblock {\rm Neurocomput } 44:285--292.

\bibitem[Barbieri and Brunnel, 2008]{Barbieri2008}
Barbieri F, Brunel N (2008{\rm{}})
\newblock Can attractor network models account for the statistics of firing during persistent activity in prefrontal cortex?
\newblock {\rm Front Neurosci } 2:114--122.

\bibitem[Bi and Poo, 1998]{Bi98}
Bi GQ, Poo MM (1998{\rm{}})
\newblock Synaptic modifications in cultured hippocampal neurons: dependence on
  spike timing, synaptic strength, and postsynaptic cell type.
\newblock {\rm J Neurosci } 18:10464--10472.

\bibitem[Bliss and Lomo, 1973]{Bliss1973}
Bliss TV, L{\o}mo T (1973{\rm{}})
\newblock Long-lasting potentiation of synaptic transmission in the dentate
  area of the anaesthetized rabbit following stimulation of the perforant path.
\newblock {\rm J Physiol } 232:331--356.

\bibitem[Brea {\rm et~al.}, 2013]{Brea2013}
Brea J, Senn W, Pfister JP (2013{\rm{}})
\newblock Matching recall and storage in sequence learning with spiking neural networks.
\newblock {\rm J Neurosci } 33:9565--9575.

\bibitem[Brown, 1914]{Brown1914}
Brown GT (1914{\rm{}})
\newblock On the nature of the fundamental activity of the nervous centre: together 
with an analysis of the conditioning of rhythmic activity in progression, and a 
theory of the evolution of function in the nervous systems.
\newblock {J Physiol } 48:18--46.

\bibitem[Buzs\'{a}ki, 1989]{Buzsaki1989}
Buzs\'{a}ki G (1989{\rm{}})
\newblock Two-stage model of memory trace formation: a role for ``noisy'' brain
  states.
\newblock {\rm Neurosci } 31:551--570.

\bibitem[Cafaro and Rieke, 2010]{Cafaro2010}
Cafaro J, Rieke F (2010{\rm{}})
\newblock Noise correlations improve response fidelity and stimulus encoding.
\newblock {\rm Nature } 468:964--967.

\bibitem[Cheng and Ji, 2013]{Cheng2013}
Cheng J, Ji D (2013{\rm{}})
\newblock Rigid firing sequences undermine spatial memory codes in a neurodegenerative mouse model.
\newblock {\rm eLife } 2:e00647.

\bibitem[Clopath {\rm et~al.}, 2010]{Clopath2010}
Clopath C, B{\"u}sing L, Vasilaki E, Gerstner W (2010{\rm{}})
\newblock Connectivity reflects coding: a model of voltage-based STDP with
  homeostasis.
\newblock {\rm Nat Neurosci } 13:344--352.

\bibitem[Contreras {\rm et~al.}, 2013]{Contreras2013}
Contreras EJB, Schjetnan AGP, Muhammad A, Bartho P, McNaughton BL, Kolb B, Gruber AJ, Luczak A (2013{\rm{}})
\newblock Formation and reverberation of sequential neural activity patterns evoked by sensory stimulation are enhanced during cortical desynchronization.
\newblock {\rm Neuron } 79:555--566.

\bibitem[Cossart {\rm et~al.}, 2003]{Cossart2003}
Cossart R, Aronov D, Yuste R (2003{\rm{}})
\newblock Attractor dynamics of network UP states in the neocortex.
\newblock {\rm Nature } 423:283--288.

\bibitem[Cossell {\rm et~al.}, 2015]{Cossell2015}
Cossell L, Iacaruso MF, Muir DR, Houlton R, Sader EN, Ko H, Hofer SB,  Mrsic-Flogel TD (2015{\rm{}})
\newblock Functional organization of excitatory synaptic strength in primary visual cortex.
\newblock {\rm Nature } 518:399--403.

\bibitem[Csicsvari {\rm et~al.}, 2000]{Csicsvari2000}
Csicsvari J, Hirase H, Mamiya A, Buzs\'{a}ki G (2000{\rm{}})
\newblock Ensemble patterns of hippocampal CA3-CA1 neurons during sharp wave-associated population events.
\newblock {\rm Neuron } 28:585--594.

\bibitem[D'amour and Froemke, 2015]{Damour2015}
D'amour JA, Froemke RC (2015{\rm{}})
\newblock Inhibitory and excitatory spike-timing-dependent plasticity in the auditory cortex.
\newblock {\rm Neuron } 86:514--528.

%\bibitem[Destexhe {\rm et~al.}, 2003]{Destexhe2003}
%Destexhe A, Rudolph M, Par\'{e} D (2003{\rm{}})
%\newblock The high-conductance state of neocortical neurons in vivo.
%\newblock {\rm Nat Rev Neurosci } 4:739--751.

\bibitem[Diba and Buzs\'{a}ki, 2007]{Diba2007}
Diba K, Buzs\'{a}ki G (2007{\rm{}})
\newblock Forward and reverse hippocampal place-cell sequences during ripples.
\newblock {Nat Neurosci } 10:1241--1242.

\bibitem[Diekelmann and Born, 2010]{Diekelmann2010}
Diekelmann S, Born J (2010{\rm{}})
\newblock The memory function of sleep.
\newblock {Nat Rev Neurosci } 11:114--126.

\bibitem[Diesmann {\rm et~al.}, 1999]{Diesmann99}
Diesmann M, Gewaltig MO, Aertsen A (1999{\rm{}})
\newblock Stable propagation of synchronous spiking in cortical neural
  networks.
\newblock {\rm Nature } 402:529--533.

\bibitem[Dragoi and Tonegawa, 2013]{Dragoi2013}
Dragoi G, Tonegawa S (2013{\rm{}})
\newblock Distinct preplay of multiple novel spatial experiences in the rat.
\newblock {\rm Proc Natl Acad Sci USA} 110:9100--9105.

%\bibitem[Ellender {\rm et~al.}, 2010]{Ellender2010}
%Ellender TJ, Nissen W, Colgin LL, Mann EO, Paulsen O (2010{\rm{}})
%\newblock Priming of hippocampal population bursts by individual perisomatic-targeting interneurons.
%\newblock {\rm J Neurosci } 30:5979--5991.

\bibitem[English {\rm et~al.}, 2014]{English2014}
  English DF, Peyrache A, Stark E, Roux L, Vallentin D, Long MA, Buzs\`{a}ki G (2014{\rm{}})
\newblock Excitation and inhibition compete to control spiking during hippocampal ripples: intracellular study in behaving mice.
\newblock {\rm J Neurosci } 34:16509--16517.

\bibitem[Felsen {\rm et~al.}, 2005]{Felsen2005}
Felsen G, Touryan J, Han F, Dan Y (2005{\rm{}})
\newblock Cortical sensitivity to visual features in natural scenes.
\newblock {\rm PLoS Biol } 3:e342.

\bibitem[Feng {\rm et~al.}, 2015]{Feng2015}
Feng T, Silva D, Foster DJ (2015{\rm{}})
\newblock Dissociation between the experience-dependent development of hippocampal theta sequences and single-trial phase precession.
\newblock {\rm J Neurosci } 35:4980--4902.

\bibitem[Foster and Wilson, 2006]{Foster2006}
Foster DJ, Wilson MA (2006{\rm{}})
\newblock Reverse replay of behavioural sequences in hippocampal place cells
  during the awake state.
\newblock {\rm Nature } 440:680--683.

\bibitem[Gerstner, 1995]{Gerstner95}
Gerstner W (1995{\rm{}})
\newblock Time structure of the activity in neural network models.
\newblock {\rm Phys Rev E } 51:738--758.

\bibitem[Gerstner {\rm et~al.}, 1996]{Gerstner96}
Gerstner W, Kempter R, van Hemmen JL, Wagner H (1996{\rm{}})
\newblock A neuronal learning rule for sub-millisecond temporal coding.
\newblock {\rm Nature } 386:76--78.

\bibitem[Goodman and Brette, 2009]{Goodman2009}
Goodman DFM, Brette R (2009{\rm{}})
\newblock The brian simulator.
\newblock {\rm Front Neurosci } 3:192--197.

\bibitem[Graupner and Brunel, 2012]{Graupner2012}
Graupner M, Brunel N (2012{\rm{}})
\newblock Calcium-based plasticity model explains sensitivity of synaptic changes to spike pattern, rate, and dendritic location.
\newblock {\rm Proc Natl Acad Sci USA } 109:3991--3996.

\bibitem[Halff {\rm et~al.}, 2014]{Halff2014}
Halff AW, G{\'o}mez-Varela D, John D, Berg DK (2014{\rm{}})
\newblock A novel mechanism for nicotinic potentiation of glutamatergic
  synapses.
\newblock {\rm J Neurosci } 34:2051--2064.

\bibitem[Hahn {\rm et~al.}, 2014]{Hahn2014}
Hahn G, Bujan AF, Fr\'egnac Y, Aertsen A, Kumar A (2014{\rm{}})
\newblock Communication through resonance in spiking neuronal networks.
\newblock {\rm PLoS Comput Biol} 10:e1003811.

\bibitem[Hanse {\rm et~al.}, 2013]{Hanse2013}
Hanse E, Seth H, Riebe I (2013{\rm{}})
\newblock AMPA-silent synapses in brain development and pathology.
\newblock {\rm Nat Rev Neurosci } 14:839--850.

\bibitem[Hasselmo, 1999]{Hasselmo1999}
Hasselmo ME (1999{\rm{}})
\newblock Neuromodulation: acetylcholine and memory consolidation.
\newblock {\rm Trends Cogn Sci } 3:351--359.

\bibitem[Hasselmo {\rm et~al.}, 1995]{Hasselmo1995}
Hasselmo ME, Schnell E, Barkai E (1995{\rm{}})
\newblock Dynamics of learning and recall at excitatory recurrent synapses and
  cholinergic modulation in rat hippocampal region CA3.
\newblock {\rm J Neurosci } 15:5249--5262.

\bibitem[Hebb, 1949]{Hebb49}
Hebb DO (1949{\rm{}})
\newblock {\rm The organization of behavior: A neuropsychological theory}.
\newblock New York.

\bibitem[Hennequin {\rm et~al.}, 2012]{Hennequin2012}
Hennequin G, Vogels TP, Gerstner W (2012{\rm{}})
\newblock Non-normal amplification in random balanced neuronal networks.
\newblock {\rm Phys Rev E } 86:011909.

\bibitem[Horn {\rm et~al.}, 2000]{Horn2000}
Horn D, Levy N, Meilijson I, Ruppin E (2000{\rm{}})
\newblock Distributed synchrony of spiking neurons in a Hebbian cell assembly.
\newblock {\rm Adv Neural Inf Process Syst } 12:129--135.

\bibitem[Jahnke {\rm et~al.}, 2013]{Jahnke2013}
Jahnke S, Memmesheimer RM, Timme M (2013{\rm{}})
\newblock Propagating synchrony in feed-forward networks.
\newblock {\rm Front Comput Neurosci } 7:153.

\bibitem[Kammerer {\rm et~al.}, 2013]{Kammerer2013}
Kammerer A, Tejero-Cantero {\'A}, Leibold C (2013{\rm{}})
\newblock Inhibition enhances memory capacity: optimal feedback, transient
  replay and oscillations.
\newblock {\rm J Comput Neurosci } 34:125--136.

\bibitem[Kappel {\rm et~al.}, 2014]{Kappel2014}
Kappel D, Nessler B, Maass W (2014{\rm{}})
\newblock STDP installs in winner-take-all circuits an online approximation to hidden Markov model learning.
\newblock {\rm PLoS Comput Biol} 10:e1003511.

\bibitem[Karlsson and Frank, 2009]{Karlsson2009}
Karlsson MP, Frank LM (2009{\rm{}})
\newblock Awake replay of remote experiences in the hippocampus.
\newblock {\rm Nature Neurosci } 12:913--918.

\bibitem[Kempter {\rm et~al.}, 1999]{Kempter99}
Kempter R, Gerstner W, van Hemmen JL (1999{\rm{}})
\newblock Hebbian learning and spiking neurons.
\newblock {\rm Phys Rev E } 59:4498.

\bibitem[Kenet {\rm et~al.}, 2003]{Kenet2003}
Kenet T, Bibitchkov D, Tsodyks M, Grinvald A, Arieli A (2003{\rm{}})
\newblock Spontaneously emerging cortical representations of visual attributes.
\newblock {\rm Nature } 425:954--956.

\bibitem[Klampfl and Maass, 2013]{Klampfl2013}
Klampfl S, Maass W (2013{\rm{}})
\newblock Emergence of dynamic memory traces in cortical microcircuit models
  through STDP.
\newblock {\rm J Neurosci } 33:11515--11529.

\bibitem[Ko {\rm et~al.}, 2011]{Ko2011}
Ko H, Hofer SB, Pichler B, Buchanan KA, Sj\"{o}str{\"o}m PJ, Mrsic-Flogel TD (2011{\rm{}})
\newblock Functional specificity of local synaptic connections in neocortical
  networks.
\newblock {\rm Nature } 473:87--91.

%\bibitem[Kremkow {\rm et~al.}, 2010]{Kremkow2010}
  %Kremkow J, Aertsen A, Kumar A (2010{\rm{}})
%\newblock Gating of signal propagation in spiking neural networks by balanced and correlated excitation and inhibition.
%\newblock {\rm J Neurosci } 30:15760--15768.

\bibitem[Kruskal {\rm et~al.}, 2013]{Kruskal2013}
Kruskal PB, Li L, MacLean JN (2013{\rm{}})
\newblock Circuit reactivation dynamically regulates synaptic plasticity in
  neocortex.
\newblock {\rm Nat Commun } 4:2574.

\bibitem[Kumar {\rm et~al.}, 2008]{Kumar2008}
Kumar A, Rotter S, Aertsen A (2008{\rm{}})
\newblock Conditions for propagating synchronous spiking and asynchronous
  firing rates in a cortical network model.
\newblock {\rm J Neurosci} 28:5268--5280.

\bibitem[Kumar {\rm et~al.}, 2010]{Kumar2010}
Kumar A, Rotter S, Aertsen A (2010{\rm{}})
\newblock Spiking activity propagation in neuronal networks: reconciling different perspectives on neural coding.
\newblock {\rm Nature Rev Neurosci} 11:615--627.

\bibitem[Lashley, 1951]{Lashley1951}
Lashley KS (1951{\rm{}})
\newblock {\rm The problem of serial order in behavior.
In: Cerebral mechanisms in behavior (Jeffress LA, ed), pp 112--131}.
\newblock New York: Wiley.

\bibitem[Lazar {\rm et~al.}, 2009]{Lazar2009}
Lazar A, Pipa G, Triesch J (2009{\rm{}})
\newblock SORN: a self-organizing recurrent neural network.
\newblock {\rm Front Comput Neurosci } 3:23.

\bibitem[Lee and Wilson, 2002]{Lee2002}
Lee AK, Wilson MA (2002{\rm{}})
\newblock Memory of sequential experience in the hippocampus during slow wave
  sleep.
\newblock {\rm Neuron } 36:1183--1194.

\bibitem[Leibold and Kempter, 2006]{Leibold2006}
Leibold C, Kempter R (2006{\rm{}})
\newblock Memory capacity for sequences in a recurrent network with biological constraints.
\newblock {\rm Neural Comput} 18:904--941.

\bibitem[Leibold and Kempter, 2008]{Leibold2008}
Leibold C, Kempter R (2008{\rm{}})
\newblock Sparseness constrains the prolongation of memory lifetime via synaptic metaplasticity.
\newblock {\rm Cereb Cortex} 18:67--77.

\bibitem[Litwin-Kumar and Doiron, 2012]{Litwin-Kumar2012}
Litwin-Kumar A, Doiron B (2012{\rm{}})
\newblock Slow dynamics and high variability in balanced cortical networks with clustered connections.
\newblock {\rm Nat Neurosci } 15:1498--1505.

\bibitem[Litwin-Kumar and Doiron, 2014]{Litwin-Kumar2014}
Litwin-Kumar A, Doiron B (2014{\rm{}})
\newblock Formation and maintenance of neuronal assemblies through synaptic plasticity.
\newblock {\rm Nat Commun } 5:5319.

\bibitem[Luczak {\rm et~al.}, 2009]{Luczak2009}
  Luczak A, Barth{\`o} P, Harris KD (2009{\rm{}})
\newblock Spontaneous events outline the realm of possible sensory responses in neocortical populations.
\newblock {\rm Neuron } 62:413--425.

\bibitem[Malenka and Bear, 2004]{Malenka2004}
Malenka RC, Bear MF (2004{\rm{}})
\newblock LTP and LTD: an embarrassment of riches.
\newblock {\rm Neuron } 44:5--21.

\bibitem[Marrosu {\rm et~al.}, 1995]{Marrosu1995}
Marrosu F, Portas C, Mascia MS, Casu MA, F{\`a} M, Giagheddu M, Imperato A, Gessa GL (1995{\rm{}})
\newblock Microdialysis measurement of cortical and hippocampal acetylcholine
  release during sleep-wake cycle in freely moving cats.
\newblock {\rm Brain Res } 671:329--332.

\bibitem[Mehring {\rm et~al.}, 2003]{Mehring2003}
Mehring C, Hehl U, Kubo M, Diesmann M, Aertsen A (2003{\rm{}})
\newblock Activity dynamics and propagation of synchronous spiking in locally
  connected random networks.
\newblock {\rm Biol Cybern } 88:395--408.

\bibitem[Memmesheimer, 2010]{Memmesheimer2010}
Memmesheimer RM (2010{\rm{}})
\newblock Quantitative prediction of intermittent high-frequency oscillations in neural networks with supralinear dendritic interactions.
\newblock {\rm Proc Natl Acad Sci USA } 107:11092--11097.

\bibitem[Moldakarimov {\rm et~al.}, 2015]{Moldakarimov2015}
Moldakarimov S, Bazhenov M, Sejnowski TJ (2015{\rm{}})
\newblock Feedback stabilizes propagation of synchronous spiking in cortical neural networks.
\newblock {\rm Proc Natl Acad Sci USA } 112:2545--2550.

\bibitem[Morrison {\rm et~al.}, 2007]{Morrison2007}
Morrison A, Aertsen A, Diesmann M (2007{\rm{}})
\newblock Spike-timing-dependent plasticity in balanced random networks.
\newblock {\rm Neural Comput } 19:1437--1467.

\bibitem[Mostafa and Indiveri, 2014]{Mostafa2014}
Mostafa H, Indiveri G (2014{\rm{}})
\newblock Sequential activity in asymmetrically coupled winner-take-all circuits.
\newblock {\rm Neural Comput } 26:1973--2004.

\bibitem[Murphy and Miller, 2009]{Murphy2009}
Murphy BK, Miller KD (2009{\rm{}})
\newblock Balanced amplification: a new mechanism of selective amplification of
  neural activity patterns.
\newblock {\rm Neuron } 61:635--648.

%\bibitem[Nakazawa {\rm et~al.}, 2004]{Nakazawa2004}
%Nakazawa K, McHugh TJ, Wilson MA, Tonegawa S (2004{\rm{}})
%\newblock NMDA receptors, place cells and hippocampal spatial memory.
%\newblock {\rm Nature Rev Neurosci} 5:361--372.

\bibitem[Okun and Lampl, 2008]{Okun2008}
Okun M, Lampl I (2008{\rm{}})
\newblock Instantaneous correlation of excitation and inhibition during ongoing
  and sensory-evoked activities.
\newblock {\rm Nat Neurosci } 11:535--537.

\bibitem[Pfister and Gerstner, 2006]{Pfister2006}
Pfister JP, Gerstner W (2006{\rm{}})
\newblock Triplets of spikes in a model of spike timing-dependent plasticity.
\newblock {\rm J Neurosci } 26:9673--9682.

\bibitem[Renart {\rm et~al.}, 2007]{Renart2007}
Renart A, Moreno-Bote R, Wang XJ, Parga N (2007{\rm{}})
\newblock Mean-driven and fluctuation-driven persistent activity in recurrent networks.
\newblock {\rm Neural Comput } 19:1--46.

\bibitem[Rezende and Gerstner, 2014]{Rezende2014}
Rezende DJ, Gerstner W (2014{\rm{}})
\newblock Stochastic variational learning in recurrent spiking networks.
\newblock {\rm Front Comput Neurosci } 8:38.

\bibitem[Roudi and Latham, 2007]{Roudi2007}
Roudi Y, Latham PE (2007{\rm{}})
\newblock A balanced memory network.
\newblock {\rm PLoS Comput Biol } 3:1679--1700.

\bibitem[Sadeh {\rm et~al.}, 2015]{Sadeh2015}
Sadeh S, Clopath C, Rotter S (2015{\rm{}})
\newblock Emergence of functional specificity in balanced networks with synaptic plasticity.
\newblock {\rm PLoS Comput Biol } 11:e1004307.

\bibitem[Sadovsky and MacLean, 2013]{Sadovsky2013}
Sadovsky AJ, MacLean JN (2013{\rm{}})
\newblock Scaling of topologically similar functional modules defines mouse
  primary auditory and somatosensory microcircuitry.
\newblock {\rm J Neurosci } 33:14048--14060.

\bibitem[Scarpetta and de Candia, 2014]{Scarpetta2014}
Scarpetta S, de Candia A (2014{\rm{}})
\newblock Alternation of up and down states at a dynamical phase-transition of a neural network with spatiotemporal attractors.
\newblock {\rm Front Syst Neurosci } 8:88.

%\bibitem[Schlingloff {\rm et~al.}, 2014]{Schlingloff2014}
%Schlingloff D, K\'ali S, Freund TF, H\'ajos N, Guly\'as AI (2014{\rm{}})
%\newblock Mechanisms of sharp wave initiation and ripple generation.
%\newblock {\rm J Neurosci } 34:11385--11398.

\bibitem[Song {\rm et~al.}, 2005]{Song2005}
Song S, Sj\"{o}str\"{o}m PJ, Reigl M, Nelson S, Chklovskii DB (2005{\rm{}})
\newblock Highly nonrandom features of synaptic connectivity in local cortical
  circuits.
\newblock {\rm PLoS Biol } 3:e68.

\bibitem[Stark {\rm et~al.}, 2015]{Stark15}
Stark E, Roux L, Eichler R, Buzs\'{a}ki G (2005{\rm{}})
\newblock Local generation of multineuronal spike sequences in
the hippocampal CA1 region.
\newblock {\rm Proc Natl Acad Sci USA} 112:10521--10526.


\bibitem[Thomas, 2015]{Thomas2015}
Thomas SA (2015{\rm{}})
\newblock Neuromodulatory signaling in hippocampus-dependent memory retrieval.
\newblock {\rm Hippocampus } 25:415--431.

\bibitem[Titchener, 1909]{Titchener1909}
Titchener EB (1909{\rm{}})
\newblock {\rm Lectures on the experimental psychology of the
  thought-processes}.
\newblock New York: Macmillan.

\bibitem[Trengove {\rm et~al.}, 2013]{Trengove2013}
Trengove C, van Leeuwen C, Diesmann M (2013{\rm{}})
\newblock High-capacity embedding of synfire chains in a cortical network
  model.
\newblock {\rm J Comput Neurosci } 34:185--209.

\bibitem[Treves and Rolls, 1991]{Treves91}
Treves A, Rolls ET (1991{\rm{}})
\newblock What determines the capacity of autoassociative memories in the brain?
\newblock {\rm Network: Comput Neural Syst } 2:371--397.

\bibitem[Tsodyks and Markram, 1997]{Tsodyks97}
Tsodyks MV, Markram H (1997{\rm{}})
\newblock The neural code between neocortical pyramidal neurons depends on neurotransmitter release probability.
\newblock {\rm Proc Natl Acad Sci USA} 94:719--723.

\bibitem[van Vreeswijk and Sompolinsky, 1996]{vanVreeswijk96}
van Vreeswijk C, Sompolinsky H (1996{\rm{}})
\newblock Chaos in neuronal networks with balanced excitatory and inhibitory
  activity.
\newblock {\rm Science } 274:1724--1726.

\bibitem[van Vreeswijk and Sompolinsky, 1998]{vanVreeswijk98}
van Vreeswijk C, Sompolinsky H (1998{\rm{}})
\newblock Chaotic balanced state in a model of cortical circuits.
\newblock {\rm Neural Comput } 10:1321--1371.

%\bibitem[Vogels and Abbott, 2009]{Vogels2009}
%Vogels TP, Abbott LF (2009{\rm{}})
%\newblock Gating multiple signals through detailed balance of excitation and inhibition in spiking networks.
%\newblock {\rm Nat Neurosci } 12:483--491.

\bibitem[Vogels {\rm et~al.}, 2011]{Vogels2011}
Vogels TP, Sprekeler H, Zenke F, Clopath C, Gerstner W (2011{\rm{}})
\newblock Inhibitory plasticity balances excitation and inhibition in sensory
  pathways and memory networks.
\newblock {\rm Science } 334:1569--1573.

\bibitem[Waddington {\rm et~al.}, 2012]{Waddington2012}
Waddington A, Appleby PA, De Kamps M, Cohen N (2012{\rm{}})
\newblock Triphasic spike-timing-dependent plasticity organizes networks to produce robust sequences of neural activity.
\newblock {\rm Front Comput Neurosci } 6:88.

\bibitem[Wallace and Kerr, 2010]{Wallace2010}
Wallace DJ, Kerr JND (2010{\rm{}})
\newblock Chasing the cell assembly.
\newblock {\rm Curr Opin Neurobiol } 20:296--305.

\bibitem[Washburn, 1916]{Washburn1916}
Washburn MF (1916{\rm{}})
\newblock {\rm Movement and mental imagery: outlines of a motor theory of the
  complexer mental processes}.
\newblock Boston: Houghton Mifflin.

\bibitem[Willshaw {\rm et~al.}, 1969]{Willshaw69}
Willshaw DJ, Buneman OP, Longuet-Higgins HC (1969{\rm{}})
\newblock Non-holographic associative memory.
\newblock {\rm Nature } 222:960--962.

\bibitem[Wilson and McNaughton, 1993]{Wilson93}
Wilson MA, McNaughton BL (1993{\rm{}})
\newblock Dynamics of the hippocampal ensemble code for space.
\newblock {\rm Science } 261:1055--1058.

\bibitem[Xue {\rm et~al.}, 2014]{Xue2014}
Xue M, Atallah BV, Scanziani M (2014{\rm{}})
\newblock Equalizing excitation-inhibition ratios across visual cortical
  neurons.
\newblock {\rm Nature } 511:596--600.

\bibitem[Zenke {\rm et~al.}, 2015]{Zenke2015}
Zenke F, Agnes EJ, Gerstner W (2015{\rm{}})
\newblock Diverse synaptic plasticity mechanisms orchestrated to form and retrieve memories in spiking neural networks.
\newblock {\rm Nature Commun } 6:6922.



\end{thebibliography}


