
\begin{thebibliography}{}

\bibitem{Abeles91}
Abeles M.
\newblock Corticonics: neural circuits of the cerebral cortex.
\newblock Cambridge, UK: Cambridge UP.; 1991.

\bibitem{AlmeidaFilho2014}
Almeida-Filho DG, Lopes-dos-Santos V, Vasconcelos NA, Miranda JG,
  Tort AB, Ribeiro S.
\newblock An investigation of Hebbian phase sequences as assembly graphs.
\newblock Front Neural Circuits. 2014;8:34.

\bibitem{Amit97}
Amit DJ, Brunel N.
\newblock Model of global spontaneous activity and local structured activity during delay periods in the cerebral cortex.
\newblock Cereb Cortex. 1997;7:237--252.

\bibitem{Atwood1999}
Atwood HL, Wojtowicz JM.
\newblock Silent synapses in neural plasticity: current evidence.
\newblock Learn Mem. 1999;6:542--571.

\bibitem{Aviel2004}
Aviel Y, Horn D, Abeles M.
\newblock Synfire waves in small balanced networks.
\newblock Neurocomput. 2004;58:123--127.

\bibitem{Aviel2003}
Aviel Y, Mehring C, Abeles M, Horn D.
\newblock On embedding synfire chains in a balanced network.
\newblock Neural Comput. 2003;15:1321--1340.

\bibitem{Aviel2002}
Aviel Y, Pavlov E, Abeles M, Horn D.
\newblock Synfire chain in a balanced network.
\newblock Neurocomput. 2002;44:285--292.

\bibitem{Azizi2013}
Azizi AH, Wiskott L, Cheng S.
\newblock A computational model for preplay in the hippocampus.
\newblock Front Comput Neurosci. 2013;7:161.

\bibitem{Barbieri2008}
Barbieri F, Brunel N.
\newblock Can attractor network models account for the statistics of firing during persistent activity in prefrontal cortex?
\newblock Front Neurosci. 2008;2:114--122.

\bibitem{Bi98}
Bi GQ, Poo MM.
\newblock Synaptic modifications in cultured hippocampal neurons: dependence on
  spike timing, synaptic strength, and postsynaptic cell type.
\newblock J Neurosci. 1998;18:10464--10472.

\bibitem{Bliss1973}
Bliss TV, L{\o}mo T.
\newblock Long-lasting potentiation of synaptic transmission in the dentate
  area of the anaesthetized rabbit following stimulation of the perforant path.
\newblock J Physiol. 1973;232:331--356.

\bibitem{Brea2013}
Brea J, Senn W, Pfister JP.
\newblock Matching recall and storage in sequence learning with spiking neural networks.
\newblock J Neurosci. 2013;33:9565--9575.

\bibitem{Brown1914}
Brown GT.
\newblock On the nature of the fundamental activity of the nervous centre: together 
with an analysis of the conditioning of rhythmic activity in progression, and a 
theory of the evolution of function in the nervous systems.
\newblock J Physiol. 1914;48:18--46.

\bibitem{Brunel2000}
Brunel N.
\newblock Dynamics of sparsely connected networks of excitatory and inhibitory spiking neurons.
\newblock J Comput Neurosci. 2000;8:183--208.

\bibitem{Bush2010}
Bush D, Philippides A, Husbands P, O'Shea M. 
\newblock Dual coding with STDP in a spiking recurrent neural network model of the hippocampus.
\newblock PLoS Comput Biol. 2010;6:e1000839.

\bibitem{Buzsaki1989}
Buzs\'{a}ki G.
\newblock Two-stage model of memory trace formation: a role for ``noisy'' brain
  states.
\newblock Neurosci. 1989;31:551--570.

\bibitem{Cafaro2010}
Cafaro J, Rieke F.
\newblock Noise correlations improve response fidelity and stimulus encoding.
\newblock Nature. 2010;468:964--967.

\bibitem{Cateau2001}
C\^ateau H, Fukai T.
\newblock Fokker--Planck approach to the pulse packet propagation in synfire chain.
\newblock Neural Net. 2001;14:675--685.

\bibitem{Cheng2013}
Cheng J, Ji D.
\newblock Rigid firing sequences undermine spatial memory codes in a neurodegenerative mouse model.
\newblock eLife. 2013;2:e00647.

\bibitem{ChengS2013}
Cheng S.
\newblock The CRISP theory of hippocampal function in episodic memory.
\newblock Front Neural Circuits. 2013;7:88.

\bibitem{Clopath2010}
Clopath C, B{\"u}sing L, Vasilaki E, Gerstner W.
\newblock Connectivity reflects coding: a model of voltage-based STDP with
  homeostasis.
\newblock Nat Neurosci. 2010;13:344--352.

\bibitem{Contreras2013}
Contreras EJB, Schjetnan AGP, Muhammad A, Bartho P, McNaughton BL, Kolb B, Gruber AJ, Luczak A.
\newblock Formation and reverberation of sequential neural activity patterns evoked by sensory stimulation are enhanced during cortical desynchronization.
\newblock Neuron. 2013;79:555--566.

\bibitem{Cossart2003}
Cossart R, Aronov D, Yuste R.
\newblock Attractor dynamics of network UP states in the neocortex.
\newblock Nature. 2003;423:283--288.

\bibitem{Cossell2015}
Cossell L, Iacaruso MF, Muir DR, Houlton R, Sader EN, Ko H, Hofer SB,  Mrsic-Flogel TD.
\newblock Functional organization of excitatory synaptic strength in primary visual cortex.
\newblock Nature. 2015;518:399--403.

\bibitem{Csicsvari1999}
Csicsvari J, Hirase H, Czurk\'{o} A, Mamiya A, Buzs\'{a}ki G.
\newblock Oscillatory coupling of hippocampal pyramidal cells and interneurons in the behaving rat.
\newblock J Neurosci. 1999;19:247--287.

\bibitem{Csicsvari2000}
Csicsvari J, Hirase H, Mamiya A, Buzs\'{a}ki G.
\newblock Ensemble patterns of hippocampal CA3-CA1 neurons during sharp wave-associated population events.
\newblock Neuron. 2000;28:585--594.

\bibitem{Damour2015}
D'amour JA, Froemke RC.
\newblock Inhibitory and excitatory spike-timing-dependent plasticity in the auditory cortex.
\newblock Neuron. 2015;86:514--528.

%\bibitem{Destexhe2003}
%Destexhe A, Rudolph M, Par\'{e} D (2003{\rm{}})
%\newblock The high-conductance state of neocortical neurons in vivo.
%\newblock {\rm Nat Rev Neurosci } 4:739--751.

\bibitem{Diba2007}
Diba K, Buzs\'{a}ki G.
\newblock Forward and reverse hippocampal place-cell sequences during ripples.
\newblock Nat Neurosci. 2007;10:1241--1242.

\bibitem{Diekelmann2010}
Diekelmann S, Born J.
\newblock The memory function of sleep.
\newblock Nat Rev Neurosci. 2010;11:114--126.

\bibitem{Diesmann99}
Diesmann M, Gewaltig MO, Aertsen A.
\newblock Stable propagation of synchronous spiking in cortical neural
  networks.
\newblock Nature. 1999;402:529--533.

\bibitem{Dragoi2011}
Dragoi G, Tonegawa S.
\newblock Preplay of future place cell sequences by hippocampal cellular assemblies.
\newblock Nature. 2011;469:397--401.

\bibitem{Dragoi2013}
Dragoi G, Tonegawa S.
\newblock Distinct preplay of multiple novel spatial experiences in the rat.
\newblock Proc Natl Acad Sci USA. 2013;110:9100--9105.

\bibitem{Draguhn98}
Draguhn A, Traub RD, Schmitz D, Jefferys JGR. 
\newblock Electrical coupling underlies high-frequency oscillations in the hippocampus in vitro.
\newblock Nature. 1998;394:189--192.

\bibitem{Ellender2010}
Ellender TJ, Nissen W, Colgin LL, Mann EO, Paulsen O.
\newblock Priming of hippocampal population bursts by individual perisomatic-targeting interneurons.
\newblock J Neurosci. 2010;30:5979--5991.

\bibitem{English2014}
  English DF, Peyrache A, Stark E, Roux L, Vallentin D, Long MA, Buzs\`{a}ki G.
\newblock Excitation and inhibition compete to control spiking during hippocampal ripples: intracellular study in behaving mice.
\newblock J Neurosci. 2014;34:16509--16517.

\bibitem{Felsen2005}
Felsen G, Touryan J, Han F, Dan Y.
\newblock Cortical sensitivity to visual features in natural scenes.
\newblock PLoS Biol. 2005;3:e342.

\bibitem{Feng2015}
Feng T, Silva D, Foster DJ.
\newblock Dissociation between the experience-dependent development of hippocampal theta sequences and single-trial phase precession.
\newblock J Neurosci. 2015;35:4980--4902.

\bibitem{Foster2006}
Foster DJ, Wilson MA.
\newblock Reverse replay of behavioural sequences in hippocampal place cells
  during the awake state.
\newblock Nature. 2006;440:680--683.

\bibitem{Gerstner95}
Gerstner W.
\newblock Time structure of the activity in neural network models.
\newblock Phys Rev E. 1995;51:738--758.

\bibitem{Gerstner96}
Gerstner W, Kempter R, van Hemmen JL, Wagner H.
\newblock A neuronal learning rule for sub-millisecond temporal coding.
\newblock Nature. 1996;386:76--78.

\bibitem{Gerstner2002}
Gerstner W, Kistler WM.
\newblock Spiking neuron models: Single neurons, population, plasticity.
\newblock Cambridge, UK: Cambridge UP.;2002.

\bibitem{Goedeke2008}
Goedeke S, Diesmann M.
\newblock The mechanism of synchronization in feed-forward neuronal networks.
\newblock New Journ Phys. 2008;10:015007.

\bibitem{Goodman2009}
Goodman DFM, Brette R.
\newblock The brian simulator.
\newblock Front Neurosci. 2009;3:192--197.

\bibitem{Graupner2012}
Graupner M, Brunel N.
\newblock Calcium-based plasticity model explains sensitivity of synaptic changes to spike pattern, rate, and dendritic location.
\newblock Proc Natl Acad Sci USA. 2012;109:3991--3996.

\bibitem{Gupta2012}
Gupta AS, van der Meer MA, Touretzky DS, Redish AD.
\newblock Segmentation of spatial experience by hippocampal theta sequences.
\newblock Nature Neurosci. 2012;15:1032--1039.

\bibitem{Guzman2016}
Guzman SJ, Schl\"{o}gl A, Frotscher M, Jonas P.
\newblock Synaptic mechanisms of pattern completion in the hippocampal CA3 network.
\newblock Science. 2016;353:1117--1123.

\bibitem{Halff2014}
Halff AW, G{\'o}mez-Varela D, John D, Berg DK.
\newblock A novel mechanism for nicotinic potentiation of glutamatergic
  synapses.
\newblock J Neurosci. 2014;34:2051--2064.

\bibitem{Hamzei2007}
Hamzei-Sichani F, Kamasawa N, Janssen WG, Yasumura T, Davidson KG, Hof PR, Wearne SL, Stewart MG, Young SR, Whittington MA, Rash JE, Traub RD.
\newblock Gap junctions on hippocampal mossy fiber axons demonstrated by thin-section electron microscopy and freeze--fracture replica immunogold labeling.
\newblock Proc Natl Acad Sci USA. 2007;104:12548-12553.

\bibitem{Hahn2014}
Hahn G, Bujan AF, Fr\'egnac Y, Aertsen A, Kumar A.
\newblock Communication through resonance in spiking neuronal networks.
\newblock PLoS Comput Biol. 2014;10:e1003811.

\bibitem{Hanse2013}
Hanse E, Seth H, Riebe I.
\newblock AMPA-silent synapses in brain development and pathology.
\newblock Nat Rev Neurosci. 2013;14:839--850.

\bibitem{Hasselmo1999}
Hasselmo ME.
\newblock Neuromodulation: acetylcholine and memory consolidation.
\newblock Trends Cogn Sci. 1999;3:351--359.

\bibitem{Hasselmo1995}
Hasselmo ME, Schnell E, Barkai E.
\newblock Dynamics of learning and recall at excitatory recurrent synapses and
  cholinergic modulation in rat hippocampal region CA3.
\newblock J Neurosci. 1995;15:5249--5262.

\bibitem{Hebb49}
Hebb DO.
\newblock The organization of behavior: A neuropsychological theory.
\newblock New York.;1949.

\bibitem{Hennequin2012}
Hennequin G, Vogels TP, Gerstner W.
\newblock Non-normal amplification in random balanced neuronal networks.
\newblock Phys Rev E. 2012;86:011909.

\bibitem{Horn2000}
Horn D, Levy N, Meilijson I, Ruppin E.
\newblock Distributed synchrony of spiking neurons in a Hebbian cell assembly.
\newblock Adv Neural Inf Process Syst. 2000;12:129--135.

\bibitem{Jahnke2013}
Jahnke S, Memmesheimer RM, Timme M.
\newblock Propagating synchrony in feed-forward networks.
\newblock Front Comput Neurosci. 2013;7:153.

\bibitem{Jahnke2015}
Jahnke S, Timme M, Memmesheimer RM.
\newblock A unified dynamic model for learning, replay, and sharp-wave/ripples.
\newblock J Neurosci. 2015;35:16236--16258.

\bibitem{Kammerer2013}
Kammerer A, Tejero-Cantero {\'A}, Leibold C.
\newblock Inhibition enhances memory capacity: optimal feedback, transient
  replay and oscillations.
\newblock J Comput Neurosci. 2013;34:125--136.

\bibitem{Kappel2014}
Kappel D, Nessler B, Maass W.
\newblock STDP installs in winner-take-all circuits an online approximation to hidden Markov model learning.
\newblock PLoS Comput Biol. 2014;10:e1003511.

\bibitem{Karlsson2009}
Karlsson MP, Frank LM.
\newblock Awake replay of remote experiences in the hippocampus.
\newblock Nature Neurosci. 2009;12:913--918.

\bibitem{Kempter99}
Kempter R, Gerstner W, van Hemmen JL.
\newblock Hebbian learning and spiking neurons.
\newblock Phys Rev E. 1999;59:4498.

\bibitem{Kenet2003}
Kenet T, Bibitchkov D, Tsodyks M, Grinvald A, Arieli A.
\newblock Spontaneously emerging cortical representations of visual attributes.
\newblock Nature. 2003;425:954--956.

\bibitem{Klampfl2013}
Klampfl S, Maass W.
\newblock Emergence of dynamic memory traces in cortical microcircuit models
  through STDP.
\newblock J Neurosci. 2013;33:11515--11529.

\bibitem{Klausberger2008}
Klausberger T, Somogyi P. 
\newblock Neuronal diversity and temporal dynamics: the unity of hippocampal circuit operations.
\newblock Science. 2008;321:53--57.

\bibitem{Ko2011}
Ko H, Hofer SB, Pichler B, Buchanan KA, Sj\"{o}str{\"o}m PJ, Mrsic-Flogel TD.
\newblock Functional specificity of local synaptic connections in neocortical
  networks.
\newblock Nature. 2011;473:87--91.

%\bibitem{Kremkow2010}
  %Kremkow J, Aertsen A, Kumar A (2010{\rm{}})
%\newblock Gating of signal propagation in spiking neural networks by balanced and correlated excitation and inhibition.
%\newblock {\rm J Neurosci } 30:15760--15768.

\bibitem{Kowalski2015}
Kowalski J, Gan J, Jonas P, Pern{\'i}a-Andrade AJ.
\newblock Intrinsic membrane properties determine hippocampal differential firing pattern in vivo in anesthetized rats.
\newblock Hippocampus. 2015;26:668--682.

\bibitem{Kruskal2013}
Kruskal PB, Li L, MacLean JN.
\newblock Circuit reactivation dynamically regulates synaptic plasticity in
  neocortex.
\newblock Nat Commun. 2013;4:2574.

\bibitem{Kullmann2011}
Kullmann DM.
\newblock Interneuron networks in the hippocampus.
\newblock Curr Opin Neurobiol. 2011;21:709--716.

\bibitem{Kumar2008}
Kumar A, Rotter S, Aertsen A.
\newblock Conditions for propagating synchronous spiking and asynchronous
  firing rates in a cortical network model.
\newblock J Neurosci. 2008;28:5268--5280.

\bibitem{Kumar2010}
Kumar A, Rotter S, Aertsen A.
\newblock Spiking activity propagation in neuronal networks: reconciling different perspectives on neural coding.
\newblock Nature Rev Neurosci. 2010;11:615--627.

\bibitem{Lashley1951}
Lashley KS.
\newblock The problem of serial order in behavior.
In: Cerebral mechanisms in behavior (Jeffress LA, ed), pp 112--131.
\newblock New York: Wiley.;1951.

\bibitem{Lazar2009}
Lazar A, Pipa G, Triesch J.
\newblock SORN: a self-organizing recurrent neural network.
\newblock Front Comput Neurosci. 2009;3:23.

\bibitem{Lee2002}
Lee AK, Wilson MA.
\newblock Memory of sequential experience in the hippocampus during slow wave
  sleep.
\newblock Neuron. 2002;36:1183--1194.

\bibitem{Leibold2006}
Leibold C, Kempter R.
\newblock Memory capacity for sequences in a recurrent network with biological constraints.
\newblock Neural Comput. 2006;18:904--941.

\bibitem{Leibold2008}
Leibold C, Kempter R.
\newblock Sparseness constrains the prolongation of memory lifetime via synaptic metaplasticity.
\newblock Cereb Cortex. 2008;18:67--77.

\bibitem{Litwin-Kumar2012}
Litwin-Kumar A, Doiron B.
\newblock Slow dynamics and high variability in balanced cortical networks with clustered connections.
\newblock Nat Neurosci. 2012;15:1498--1505.

\bibitem{Litwin-Kumar2014}
Litwin-Kumar A, Doiron B.
\newblock Formation and maintenance of neuronal assemblies through synaptic plasticity.
\newblock Nat Commun. 2014;5:5319.

\bibitem{Louie2001}
Louie K, Wilson MA.
\newblock Temporally structured replay of awake hippocampal ensemble activity during rapid eye movement sleep.
\newblock Neuron. 2001;29:145--156.

\bibitem{Luczak2009}
  Luczak A, Barth{\`o} P, Harris KD.
\newblock Spontaneous events outline the realm of possible sensory responses in neocortical populations.
\newblock Neuron. 2009;62:413--425.

\bibitem{Malenka2004}
Malenka RC, Bear MF.
\newblock LTP and LTD: an embarrassment of riches.
\newblock Neuron. 2004;44:5--21.

\bibitem{Malerba2016}
Malerba P, Krishnan GP, Fellous JM, Bazhenov M.
\newblock Hippocampal CA1 ripples as inhibitory transients.
\newblock PLoS Comput Biol. 2016;12:e1004880.

\bibitem{Marrosu1995}
Marrosu F, Portas C, Mascia MS, Casu MA, F{\`a} M, Giagheddu M, Imperato A, Gessa GL.
\newblock Microdialysis measurement of cortical and hippocampal acetylcholine
  release during sleep-wake cycle in freely moving cats.
\newblock Brain Res. 1995;671:329--332.

\bibitem{Mehring2003}
Mehring C, Hehl U, Kubo M, Diesmann M, Aertsen A.
\newblock Activity dynamics and propagation of synchronous spiking in locally
  connected random networks.
\newblock Biol Cybern. 2003;88:395--408.

\bibitem{Memmesheimer2010}
Memmesheimer RM.
\newblock Quantitative prediction of intermittent high-frequency oscillations in neural networks with supralinear dendritic interactions.
\newblock Proc Natl Acad Sci USA. 2010;107:11092--11097.

\bibitem{Mishra2016}
Mishra RK, Kim S, Guzman SJ, Jonas P.
\newblock Symmetric spike timing-dependent plasticity at CA3-CA3 synapses optimizes storage and recall in autoassociative networks.
\newblock Nat Commun. 2016;7:11552.

\bibitem{Moldakarimov2015}
Moldakarimov S, Bazhenov M, Sejnowski TJ.
\newblock Feedback stabilizes propagation of synchronous spiking in cortical neural networks.
\newblock Proc Natl Acad Sci USA. 2015;112:2545--2550.

\bibitem{Monasson2014}
Monasson R, Rosay S. 
\newblock Crosstalk and transitions between multiple spatial maps in an attractor neural network model of the hippocampus: Collective motion of the activity.
\newblock Phys Rev E. 2014;89:032803.

\bibitem{Morrison2007}
Morrison A, Aertsen A, Diesmann M.
\newblock Spike-timing-dependent plasticity in balanced random networks.
\newblock Neural Comput. 2007;19:1437--1467.

\bibitem{Mostafa2014}
Mostafa H, Indiveri G.
\newblock Sequential activity in asymmetrically coupled winner-take-all circuits.
\newblock Neural Comput. 2014;26:1973--2004.

\bibitem{Murphy2009}
Murphy BK, Miller KD.
\newblock Balanced amplification: a new mechanism of selective amplification of
  neural activity patterns.
\newblock Neuron. 2009;61:635--648.

%\bibitem{Nakazawa2004}
%Nakazawa K, McHugh TJ, Wilson MA, Tonegawa S (2004{\rm{}})
%\newblock NMDA receptors, place cells and hippocampal spatial memory.
%\newblock {\rm Nature Rev Neurosci} 5:361--372.

\bibitem{Okun2008}
Okun M, Lampl I.
\newblock Instantaneous correlation of excitation and inhibition during ongoing
  and sensory-evoked activities.
\newblock Nat Neurosci. 2008;11:535--537.

\bibitem{Omura2015}
Omura Y, Carvalho MM, Inokuchi K, Fukai T.
\newblock A lognormal recurrent network model for burst generation during hippocampal sharp waves.
\newblock J Neurosci. 2015;35:14585--145601.

\bibitem{Pfister2006}
Pfister JP, Gerstner W.
\newblock Triplets of spikes in a model of spike timing-dependent plasticity.
\newblock J Neurosci. 2006;26:9673--9682.

\bibitem{Poe2010}
Poe GR, Walsh CM, Bjorness TE.
\newblock Cognitive neuroscience of sleep.
\newblock Progr Brain Res. 2010;185:1.

\bibitem{Rapp96}
Rapp PR, Gallagher M.
\newblock Preserved neuron number in the hippocampus of aged rats with spatial learning deficits.
\newblock Proc Natl Acad Sci USA. 1996;93:9926--9930.

\bibitem{Renart2007}
Renart A, Moreno-Bote R, Wang XJ, Parga N.
\newblock Mean-driven and fluctuation-driven persistent activity in recurrent networks.
\newblock Neural Comput. 2007;19:1--46.

\bibitem{Rezende2014}
Rezende DJ, Gerstner W.
\newblock Stochastic variational learning in recurrent spiking networks.
\newblock Front Comput Neurosci. 2014;8:38.

\bibitem{Ricciardi77}
Ricciardi LM.
\newblock Diffusion processes and related topics on biology.
\newblock Berlin: Springer.;1977.

\bibitem{Romani2015}
Romani S, Tsodyks M.
\newblock Short-term plasticity based network model of place cells dynamics.
\newblock Hippocampus. 2015;25:94--105.

\bibitem{Roudi2007}
Roudi Y, Latham PE.
\newblock A balanced memory network.
\newblock PLoS Comput Biol. 2007;3:1679--1700.

\bibitem{Sadeh2015}
Sadeh S, Clopath C, Rotter S.
\newblock Emergence of functional specificity in balanced networks with synaptic plasticity.
\newblock PLoS Comput Biol. 2015;11:e1004307.

\bibitem{Sadovsky2013}
Sadovsky AJ, MacLean JN.
\newblock Scaling of topologically similar functional modules defines mouse
  primary auditory and somatosensory microcircuitry.
\newblock J Neurosci. 2013;33:14048--14060.

\bibitem{Scarpetta2014}
Scarpetta S, de Candia A.
\newblock Alternation of up and down states at a dynamical phase-transition of a neural network with spatiotemporal attractors.
\newblock Front Syst Neurosci. 2014;8:88.

\bibitem{Schlingloff2014}
Schlingloff D, K\'ali S, Freund TF, H\'ajos N, Guly\'as AI.
\newblock Mechanisms of sharp wave initiation and ripple generation.
\newblock J Neurosci. 2014;34:11385--11398.

\bibitem{Schmitz2001}
Schmitz D, Schuchmann S, Fisahn A, Draguhn A, Buhl EH, Petrasch-Parwez E, Dermietzel R, Heinemann U, Traub RD.
\newblock Axo-axonal coupling: a novel mechanism for ultrafast neuronal communication.
\newblock Neuron. 2001;13:831--840.

\bibitem{Softky1993}
Softky WR, Koch C.
\newblock The highly irregular firing of cortical cells is inconsistent with temporal integration of random EPSPs.
\newblock J Neurosci. 1993;13:4--50.

\bibitem{Song2005}
Song S, Sj\"{o}str\"{o}m PJ, Reigl M, Nelson S, Chklovskii DB.
\newblock Highly nonrandom features of synaptic connectivity in local cortical
  circuits.
\newblock PLoS Biol. 2005;3:e68.

\bibitem{Stark2015}
Stark E, Roux L, Eichler R, Buzs\'{a}ki G.
\newblock Local generation of multineuronal spike sequences in
the hippocampal CA1 region.
\newblock Proc Natl Acad Sci USA. 2005;112:10521--10526.

\bibitem{Taxidis2012}
Taxidis J, Coombes S, Mason R, Owen MR.
\newblock Modeling sharp-wave ripple complexes through a CA3-CA1 network model with chemical synapses.
\newblock Hippocampus. 2012;22:995--1017.

\bibitem{Thomas2015}
Thomas SA.
\newblock Neuromodulatory signaling in hippocampus-dependent memory retrieval.
\newblock Hippocampus. 2015;25:415--431.

\bibitem{Titchener1909}
Titchener EB.
\newblock Lectures on the experimental psychology of the
  thought-processes.
\newblock New York: Macmillan.;1909.

\bibitem{Traub2012}
Traub RD, Schmitz D, Maier N, Whittington MA, Draguhn A. 
\newblock Axonal properties determine somatic firing in a model of in vitro CA1 hippocampal sharp wave/ripples and persistent gamma oscillations.
\newblock Eur J Neurosci. 2012;36:2650--2660.

\bibitem{Trengove2013}
Trengove C, van Leeuwen C, Diesmann M.
\newblock High-capacity embedding of synfire chains in a cortical network
  model.
\newblock J Comput Neurosci. 2013;34:185--209.

%\bibitem{Treves91}
%Treves A, Rolls ET.
%\newblock What determines the capacity of autoassociative memories in the brain?
%\newblock Network: Comput Neural Syst. 1991;2:371--397.

\bibitem{Tsodyks97}
Tsodyks MV, Markram H.
\newblock The neural code between neocortical pyramidal neurons depends on neurotransmitter release probability.
\newblock Proc Natl Acad Sci USA. 1997;94:719--723.

\bibitem{vanVreeswijk96}
van Vreeswijk C, Sompolinsky H.
\newblock Chaos in neuronal networks with balanced excitatory and inhibitory
  activity.
\newblock Science. 1996;274:1724--1726.

\bibitem{vanVreeswijk98}
van Vreeswijk C, Sompolinsky H.
\newblock Chaotic balanced state in a model of cortical circuits.
\newblock Neural Comput. 1998;10:1321--1371.

%\bibitem{Vogels2009}
%Vogels TP, Abbott LF (2009{\rm{}})
%\newblock Gating multiple signals through detailed balance of excitation and inhibition in spiking networks.
%\newblock {\rm Nat Neurosci } 12:483--491.

\bibitem{Vladimirov2013}
Vladimirov N, Tu Y, Traub RD. 
\newblock Synaptic gating at axonal branches, and sharp-wave ripples with replay: a simulation study.
\newblock Eur J Neurosci. 2013;38:3435--3447.

\bibitem{Vogels2011}
Vogels TP, Sprekeler H, Zenke F, Clopath C, Gerstner W.
\newblock Inhibitory plasticity balances excitation and inhibition in sensory
  pathways and memory networks.
\newblock Science. 2011;334:1569--1573.

\bibitem{Waddington2012}
Waddington A, Appleby PA, De Kamps M, Cohen N.
\newblock Triphasic spike-timing-dependent plasticity organizes networks to produce robust sequences of neural activity.
\newblock Front Comput Neurosci. 2012;6:88.

\bibitem{Wallace2010}
Wallace DJ, Kerr JND.
\newblock Chasing the cell assembly.
\newblock Curr Opin Neurobiol. 2010;20:296--305.

\bibitem{Washburn1916}
Washburn MF.
\newblock Movement and mental imagery: outlines of a motor theory of the
  complexer mental processes.
\newblock Boston: Houghton Mifflin.;1916.

\bibitem{West91}
West MJ, Slomianka LHJG, Gundersen HJG.
\newblock Unbiased stereological estimation of the total number of neurons in the subdivisions of the rat hippocampus using the optical fractionator.
\newblock Anat Record. 1991; 231:482--497.

\bibitem{Willshaw69}
Willshaw DJ, Buneman OP, Longuet-Higgins HC.
\newblock Non-holographic associative memory.
\newblock Nature. 1969;222:960--962.

\bibitem{Wilson93}
Wilson MA, McNaughton BL.
\newblock Dynamics of the hippocampal ensemble code for space.
\newblock Science. 1993;261:1055--1058.

\bibitem{Xue2014}
Xue M, Atallah BV, Scanziani M.
\newblock Equalizing excitation-inhibition ratios across visual cortical
  neurons.
\newblock Nature. 2014;511:596--600.

\bibitem{Zenke2015}
Zenke F, Agnes EJ, Gerstner W.
\newblock Diverse synaptic plasticity mechanisms orchestrated to form and retrieve memories in spiking neural networks.
\newblock Nature Commun. 2015;6:6922.

\end{thebibliography}

